The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-24 paper/paper.tex
cleaned up tables + its captions

\caption{\label{tab:age-table}Age Distribution of the NLSY79 samples}
\centering
\begin{tabular}[t]{rr}
\toprule
Age & Number of Sample\\
\midrule
15 & 1265\\
16 & 1550\\
17 & 1600\\
18 & 1530\\
19 & 1662\\
20 & 1722\\
21 & 1677\\
22 & 1680\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:gender-race-table}Gender and Race Distribution of the NLSY79 Samples}
\centering
\begin{tabular}[t]{lllll}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Race} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-4}
Gender & Hispanic & Black & Non-Black, Non-Hispanic & Total\\
\midrule
Male & 1000 (15.62\%) & 1613 (25.19\%) & 3790 (59.19\%) & 6403 (100.00\%)\\
Female & 1002 (15.95\%) & 1561 (24.84\%) & 3720 (59.21\%) & 6283 (100.00\%)\\
Total & 2002 (15.78\%) & 3174 (25.02\%) & 7510 (59.20\%) & 12686 (100.00\%)\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:age-table}The frequency table of the age at the start of the survey (?CHECK) in the full NSLY79 data}
\centering
\begin{tabular}[t]{rr}
\toprule
Age & Number of individuals\\
\midrule
15 & 1,265\\
16 & 1,550\\
17 & 1,600\\
18 & 1,530\\
19 & 1,662\\
20 & 1,722\\
21 & 1,677\\
22 & 1,680\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:gender-race-table}The contingency table for gender and race for the full NLSY79 data.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Race} & \multicolumn{1}{c}{ } \\
\cmidrule(l{3pt}r{3pt}){2-4}
Gender & Hispanic & Black & Non-Black, Non-Hispanic & Total\\
\midrule
Male & 1,000 (15.62\%) & 1,613 (25.19\%) & 3,790 (59.19\%) & 6,403 (100.00\%)\\
Female & 1,002 (15.95\%) & 1,561 (24.84\%) & 3,720 (59.21\%) & 6,283 (100.00\%)\\
\midrule
Total & 2,002 (15.78\%) & 3,174 (25.02\%) & 7,510 (59.20\%) & 12,686 (100.00\%)\\
\bottomrule
\end{tabular}
\end{table}
